Supplementary Figures relative to the SVA-DEA benchmark

### 2020-08-04 supplementary_figures/supp_svadea.Rmd
updated sva-dea supp

suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(pipeComp)
  library(grid)
  library(ComplexHeatmap)
})
theme_set(theme_cowplot(font_size = 12))
res2 <- res1 <- res <- readRDS("../svadea/results/aggregated.rds")
res1$evaluation$dea <- lapply(res1$evaluation$dea, FUN=function(x){
  x[which(x$k==1),]
})
res2$evaluation$dea <- lapply(res2$evaluation$dea, FUN=function(x){
  x[which(x$k==2 | x$sva.method=="none"),]
})
```

@@

```{r, fig.width=8.5, fig.height=8.5}
plot_grid(
  dea_evalPlot_curve(res1, agg.by=c("dea.method","filt","minCount"), shapeBy = "dea.method", colourBy = c("filter")) + ggtitle("Using 1 SV"),
  dea_evalPlot_curve(res1, agg.by=c("sva.method","filt","minCount"), shapeBy = "sva.method", colourBy = c("filter")) + ggtitle("Using 1 SV"),
  dea_evalPlot_curve(res2, agg.by=c("sva.method")) + ggtitle("Using 2 SVs"),
  nrow=3, labels=LETTERS[1:3]
)
```

### Fig S`r getFigNb()`
Accuracy of the differential expression analysis across combinations of: **A:** filters and DEA methods (using max 1 variable), **B:** filters and SVA methods (using max 1 variable), **C:** SVA methods (using 2 variables). In **C**, filled points indicate a nominal FDR below the observed FDR.

>>>>

suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(pipeComp)
  library(grid)
  library(ComplexHeatmap)
})
theme_set(theme_cowplot(font_size = 12))
res12 <- res012 <- res0 <- res1 <- res <- readRDS("../svadea/results/aggregated.rds")
res0$evaluation$dea <- lapply(res$evaluation$dea, FUN=function(x){
  x[which(x$sva.method=="none"),]
})
res1$evaluation$dea <- lapply(res$evaluation$dea, FUN=function(x){
  x[which(x$k==1 & x$sva.method!="none"),]
})
res012$evaluation$dea <- lapply(res$evaluation$dea, FUN=function(x){
  x$k[x$sva.method=="none"] <- NA
  x[which(is.na(x$k) | x$k==2 | x$k==1),]
})
res12$evaluation$dea <- lapply(res$evaluation$dea, FUN=function(x){
  x$k[x$sva.method=="none"] <- NA
  x[which(x$k==2 | x$k==1),]
})
```

@@

```{r, fig.width=8.5, fig.height=8.5}
plot_grid(
  dea_evalPlot_curve(res0, agg.by=c("dea.method","filt","minCount"), shapeBy = "dea.method", colourBy = c("filter")),
  dea_evalPlot_curve(res12, agg.by=c("dea.method","filt","minCount"), shapeBy = "dea.method", colourBy = c("filter")),
  dea_evalPlot_curve(res012, agg.by=c("dea.method","sva.method"), shapeBy="dea.method", colourBy = c("sva.method")),
  nrow=3, labels=LETTERS[1:3]
)
```

### Fig S`r getFigNb()`
Accuracy of the differential expression analysis across combinations of: **A:** filters and DEA methods (without any SVA-step), **B:** filters and DEA methods (average across the different SVA strategies using either 1 or 2 surrogate variables), **C:** DEA and SVA methods (using one or two surrogate variables).
